Lake Photic Zone Temperature accross the Conterminous United States

### 2019-08-12 manuscript/manuscript.Rmd
Adding to discussion

In addition to the several average air temperature variables, we included land-use/land cover variables.  Specifically, we calculated the percent impervious surface for a 3km lake buffer and a measure of shoreline development (need to look at Jeff’s package to see how this is measured).  This variables were included based on the assumption that higher amounts of development and therefore impervious surface surrounding a lake would lead to higher temperatures in lakes.  Yet neither of these variables were selected in the final model.  Even though the land-use variables were not selected that does not mean development and impervious were not impactful.  This urban-heat effect on lakes may have been adequately captured in the average ambient air temperature.  Therefore, making the land-use variables redundant.  Regardless these variables did not independently contribute to the model’s accuracy.

>>>>

In addition to the several derived air temperature variables, we included land-use/land cover variables in our initial variable selection process.  Specifically, we calculated the percent impervious surface for a 3km lake buffer and a measure of shoreline development (need to look at Jeff’s package to see how this is measured).  This variables were included based on the hypothesis that higher amounts of development and therefore impervious surface surrounding a lake would lead to higher temperatures in lakes.  Yet neither of these variables were selected in the final model.  Even though the land-use variables were not selected that does not mean development and impervious are not impactful.  This urban-heat effect on lakes may have been adequately captured in the average ambient air temperature.  Therefore, making the land-use variables redundant.  Regardless these variables did not independently contribute to the model’s accuracy.
